### 2017-11-07 submission/manuscript.Rmd
complete adding figure legend

**Figure 6: **

>>>>

**Figure 6: Power and Effect Size Analysis of Studies Included.** A) Power based on effect size for studies with Adenoma individuals. B) Power based on effect size for studies with Carcinoma individuals. C) The estimated sample number needed for each arm of each study to detect aneffect size of 1-30%. The dotted red lines in A) and B) represent the generally used power of 0.8.

### 2017-11-07 submission/manuscript.tex
complete adding figure legend

\textbf{Figure 6: }

>>>>

\textbf{Figure 6: Power and Effect Size Analysis of Studies Included.}
A) Power based on effect size for studies with Adenoma individuals. B)
Power based on effect size for studies with Carcinoma individuals. C)
The estimated sample number needed for each arm of each study to detect
aneffect size of 1-30\%. The dotted red lines in A) and B) represent the
generally used power of 0.8.
